---
title: "Figures and Tables Vargas et al"
subtitle: "Not published"
author: "Camila Vargas"
date: "17 de febrero de 2019"
output: pdf_document
---
## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(here)
library(plotrix)
library(RColorBrewer)
library(cowplot) #theme_set(theme_cowplot())
library(ggrepel)
library(scales)
library(knitr)
library(kableExtra)


# my_palette <-  c(brewer.pal(9, "Blues")[c(2,4,6,8)])
# my_palette_2 <- c(brewer.pal(9, "GnBu")[c(4,5,6,7)])
my_palette_3 <- c(brewer.pal(9, "Blues")[3], brewer.pal(9, "GnBu")[c(5,6,7)])
#my_palette_3:
#"#7BCCC4" verde
#"#4EB3D3" azul mar
#"#2B8CBE" azul oscuro
#"#C6DBEF" celeste

```


# Methods

Figure 1

```{r Women participation in ssf in Chile, echo = FALSE, warning=FALSE, message=FALSE, fig.cap= 'Women participation in small-scale fisheires in Chile. A) Percentage of women officially registered in the National Fisheries Service (RPA) through time.  B) Number of mixed gender, only-women and only men associations oficially registered per year.Data source: SERNAPESCA, 2017.'}

##Percentage of women in ssf from 2004 to 2016

rpa_yearly_women <- read.csv(here("data/women_men_ssf_chile_yearly.csv")) %>% select(year, pct_women) %>% 
  filter(year == 2004:2016)
  
pct_women_plot <- ggplot(rpa_yearly_women, aes(x= year, y= pct_women/100))+
  geom_line(color = "#7BCCC4", size = 1.5)+
  theme_classic()+
  scale_x_continuous(breaks = seq(2004, 2016, 1))+
  scale_y_continuous(labels=scales::percent)+
  xlab("Year")+
  ylab("Percentage of women")+
  theme(axis.title = element_text(size = 10, face = "bold"))
  
#plot(pct_women_plot)


##RPA Associations by gender

rpa_association <- read.csv(here("data/rpa_associations_yearly.csv")) %>% 
  select(-total) %>% 
  gather(key = Gender, value = number, 2:4) %>% 
  mutate(Gender = fct_relevel(Gender,"Women", "Men", "Mixed")) %>% 
  filter(year!=2017)

association_plot <- ggplot(rpa_association)+
  geom_bar(aes(x= year, y= number, fill = Gender), stat = "identity")+
  theme_classic()+
  scale_fill_manual(values = c("#7BCCC4", "#C6DBEF","#4EB3D3"))+ #2B8CBE
  labs(y= "Number of associations", x="Year")+
  scale_x_continuous(breaks = seq(2004, 2016, 1))+
  theme(axis.title = element_text(size = 10, face = "bold"),
         legend.position="bottom", 
        legend.box = "horizontal")
        #axis.text.x = element_text(angle = 30))

##axis.text.x = element_text(size = 10, color = "black")

#plot(association_plot)

title_figure_method <- ggdraw() + draw_label("Women Participation in Small-scale Fisheries in Chile", fontface='bold')

figure_method <- plot_grid(pct_women_plot,association_plot, labels = c("A", "B"), nrow= 2 , align = "v")

#plot(figure_method)


figure_method_title <- plot_grid(title_figure_method, figure_method, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
  #draw_label("Data Source: SERNAPESCA, 2017", size = 9, fontface = "italic", x=0.87, y=0.03)

plot(figure_method_title)

##ggplot2::ggsave("women_ssf_chile.png", plot = figure_method_title)


##Activity Men and women

fishers_activity_2016 <- read_csv(here("data/fishers_activity_rpa.csv"))%>%
   filter(year == 2016) %>% 
  group_by(gender) %>% 
  mutate(total_gender = sum(number)) %>% 
  ungroup() %>% 
  mutate(pct_per_gender = (number/total_gender)*100) %>% 
  mutate(Activity = ifelse(Activity=="Gleaner", "Shore gatherer", Activity))
 


fishers_activity_16_plot <- ggplot(fishers_activity_2016)+
  geom_bar(aes(x= gender, 
               y= pct_per_gender/100, 
               fill = Activity),
           stat = "identity",
           width = 0.6)+
  theme_classic()+
  scale_y_continuous(labels=scales::percent)+
  coord_flip()+
  scale_fill_manual(values = c("#C6DBEF", "#7BCCC4", "#4EB3D3", "#2B8CBE"))+
  scale_x_discrete(labels=c("Men (n = 121,634)", "Women (n = 29,952)"))+
  ylab("Percentage of RPA")+
  ggtitle("Percentage of men and women's registers in each fishery activity")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"))

fishers_activity_legend <- ggdraw(fishers_activity_16_plot)+
  draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.87, y=0.02)


plot(fishers_activity_16_plot)



```


# Results

```{r import data, echo = FALSE, message= FALSE, warning= FALSE}
## Import data
social_capital_average <- read_csv(here("data/social_capital_average.csv"))

raw_data <- read_excel(here("data/vargas_gender_data.xlsx"), range ="A1:AG116") %>%  mutate(activities = as.numeric(activities),
         conflict = as.numeric(conflict)) %>% 
  left_join(social_capital_average, by= "folio") ##OJO!! social_capital_average

# Based on the analysis done in the file GENDER.R we concluded that there are significant diferences among groups in attributes such as:
# - Leadership
# - Entrepreneurship
# - Participation in Activities
# 
# Non-significant differences
# - Trust
# - Norms
# - Social Capital

##Based on social_capital_analysis.Rmd
#Non-significat difference
#Social capital

```

Fig caption: Results from Kruskal-Wallis test showed significant differences in Leadership "(p= 0.0005)", Entrepreneurship "(p=0.002)", Participation in Activities "(p=<0.0001)", but not in Trust "(p=0.245)", Norm accomplishments "(p=0.272)", Social Capital "(p=0.08)". Letters on the top of the bars represent Dunn’s posteriori tests' results.

```{r association level vriables,  echo = FALSE, warning=FALSE, message=FALSE, fig.cap= 'Average degree in which groups perceive association-level variables relevant for collective action. Scores go from 0 (nothing at all) to 20 (very much).'}


## Average degree in which pariticipants percieve group attributes.

##calcualting mean, sd and se
assoc_scale_summary <- raw_data %>% 
  select("Type of Association"= type_organization, Leadership = leadership, Entrepreneurship = entrepreneurship, "Participation in Activities" = activities, Trust = trust, "Norm Compliance" = norms, "Social Capital" = soc_capital) %>% 
  gather(key = attribute, value = value, 2:7) %>% 
  group_by(`Type of Association`, attribute) %>% 
  group_by(N = n(), add = TRUE) %>% ## adds the n for each type of association
  summarise_all(funs(mean, sd, std.error), na.rm = TRUE) %>% 
  ungroup() %>% 
  mutate( `Type of Association` = recode(`Type of Association`, MixedM = "Mixed - M (n=31)", MixedW = "Mixed - W (n=29)", Men = "Men (n=25)", Women = "Women (n=30)")) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Women (n=30)" & attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities"), "a",NA )) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Men (n=25)" & attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities"), "b",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - W (n=29)" & attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities"), "a",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - M (n=31)" & attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities"), "ab",signif_diff)) %>% 
   mutate("Type of Association" = fct_relevel(`Type of Association`, c("Women (n=30)", "Men (n=25)", "Mixed - W (n=29)", "Mixed - M (n=31)")),
         attribute = fct_relevel(attribute, c("Leadership", "Entrepreneurship", "Participation in Activities", "Trust", "Norm Compliance", "Social Capital")))

  
View(assoc_scale_summary)

#plot (Social Capital; Entrepreneur; Leadership)

signficant_diff <- ggplot(assoc_scale_summary %>% 
                              filter(attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities")),
                            aes(`Type of Association`, mean)) +
   geom_bar(aes(fill=`Type of Association`), stat = "identity") +
  geom_errorbar(aes(ymin = mean - std.error, ymax = mean +std.error), width=0.2) +
  geom_text_repel(aes(y=mean+std.error+0.2, label = signif_diff), 
                  nudge_y = 0.5,
                  direction = "x",
                  vjust = 0,
                  hjust = 0.5,
                  segment.colour = "transparent")+
  geom_hline(yintercept = 10, linetype = "dotted")+
  theme_classic() +
  facet_wrap(~attribute) +
  scale_fill_manual(values = c("#7BCCC4", "#4EB3D3", "#2B8CBE", "#C6DBEF"))+
  #scale_fill_brewer(palette = "BuGn")+ #find a good color
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position="none", 
        legend.box = "horizontal")

no_diff <- ggplot(assoc_scale_summary %>% 
                              filter(attribute %in% c("Norm Compliance", "Social Capital","Trust")),
  aes(`Type of Association`, mean)) +
   geom_bar(aes(fill=`Type of Association`), stat = "identity") +
  geom_errorbar(aes(ymin = mean - std.error, ymax = mean +std.error), width=0.2) +
  geom_hline(yintercept = 10, linetype = "dotted")+
  theme_classic() +
  facet_wrap(~attribute) +
  scale_fill_manual(values = c("#7BCCC4", "#4EB3D3", "#2B8CBE", "#C6DBEF"))+
  #scale_fill_brewer(palette = "BuGn")+ #find a good color
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position="bottom", 
        legend.box = "horizontal")+
  expand_limits(y = 20)
  #labs(caption = "(Vargas et al, unpublished data)", element_text(face = "italic", size = 7))

##Both plot plotted together
figure_assoc_att <- plot_grid(signficant_diff, no_diff, labels = c("A", "B"), nrow = 2, align = "v")

title_figure_assoc_att <-  ggdraw() + draw_label("Perception on association related variables", fontface='bold')

figure_assoc_att_legend <- ggdraw(figure_assoc_att)+
  draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.9, y=0.02)

figure_assoc_att_title <- plot_grid(title_figure_assoc_att, figure_assoc_att_legend, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins

plot(figure_assoc_att_title)


```




Fig caption
Average degree in which groups evaluate social performance indicators: Efficiency (p<0,0001); (Cooperation p=0,002) and (Conflict Resolution p=0,436). Scores go from 0 (nothing at all) to 20 (very much). Significant differences are represented by different letters and analyzed with Kruskal-Wallis test and Dunn’s posteriori tests.


```{r  Social performance vriables,  echo = FALSE, warning=FALSE, message=FALSE, fig.cap='hola'}
#Average degree in which groups evaluate social performance indicators


soc_perform_summary<- raw_data %>% 
  select("Type of Association"= type_organization, Efficiency = efficiency, Cooperation = cooperation, "Conflict Resolution" = conflict) %>% 
  gather(key = attribute, value = value, 2:4) %>% 
  group_by(`Type of Association`, attribute) %>% 
  group_by(N = n(), add = TRUE) %>% ## adds the n for each type of association
  summarise_all(funs(mean, sd, std.error), na.rm = TRUE) %>% 
  ungroup() %>% 
  mutate( `Type of Association` = recode(`Type of Association`, MixedM = "Mixed - M (n=31)", MixedW = "Mixed - W (n=29)", Men = "Men (n=25)", Women = "Women (n=30)")) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Women (n=30)" & attribute %in% c("Efficiency", "Cooperation"), "a",NA )) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Men (n=25)" & attribute %in% c("Efficiency", "Cooperation"), "b",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - W (n=29)" & attribute %in% c("Efficiency", "Cooperation"), "a",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - M (n=31)" & attribute == "Cooperation", "ab",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - M (n=31)" & attribute == "Efficiency", "a",signif_diff)) %>% 
  mutate("Type of Association" = fct_relevel(`Type of Association`, c("Women (n=30)", "Men (n=25)", "Mixed - W (n=29)", "Mixed - M (n=31)")),
         attribute = fct_relevel(attribute, c("Efficiency", "Cooperation", "Conflict Resolution")))
  
View(soc_perform_summary)


soc_perform_plot<- ggplot(soc_perform_summary, aes(`Type of Association`, mean)) +
   geom_bar(aes(fill=`Type of Association`), stat = "identity") +
  geom_errorbar(aes(ymin = mean - std.error, ymax = mean +std.error), width=0.2) +
  geom_text_repel(aes(y=mean+std.error, label = signif_diff), 
                  nudge_y = 0.5,
                  direction = "x",
                  vjust = 0,
                  hjust = 0.5,
                  segment.colour = "transparent")+
  geom_hline(yintercept = 10, linetype = "dotted")+ #color = "gray"
  theme_classic() +
  facet_wrap(~attribute) +
  scale_fill_manual(values = c("#7BCCC4", "#4EB3D3", "#2B8CBE", "#C6DBEF"))+
  #scale_fill_viridis(discrete = T, option = "D")+
  #scale_fill_brewer(palette = "BuGn")+ #find a good color
  #ggtitle ("Small-scale Fisher's Perception variables of social performance outcomes of their associatons")+
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position="bottom", 
        legend.box = "horizontal")+
  expand_limits(y = 20) #y-axis goes to up to 20
  
title_soc_perform <- ggdraw()+draw_label("Perception on social performance variables", fontface='bold')

 
soc_perf_legend <- ggdraw(soc_perform_plot)+
  draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.9, y=0.02)

soc_per_plot_title <- plot_grid(title_soc_perform, soc_perf_legend, ncol=1, rel_heights=c(0.1, 1)) 


plot(soc_per_plot_title)
```


## Motivations

```{r}
motivations <- read_csv(here::here("data/fishers_motivations.csv")) %>% 
  gather(key = Gender, value = percentage, 2:3) 

motivations_plot <- ggplot(motivations)+
  geom_bar(aes(x = Motivation, 
               y = percentage, 
               fill=Gender), 
           stat = "identity",
           position = "fill")+
  coord_flip()+
  scale_y_continuous(labels=scales::percent)+
  scale_fill_manual(values = c("#4EB3D3", "#7BCCC4"),
                    label = c("Men (n = 53)", "Women (n = 62)"), "Gender")+
  ylab("Percentage")+
  ggtitle("Women and Men's motivations to participate in SSF associations")+
  theme(plot.title = element_text(hjust = 0.5),
        axis.title = element_text(face = "bold"),
        axis.text.y =element_text(size = 10))

motivation_legend <- ggdraw(motivations_plot)+
  draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.9, y=0.02)


plot(motivation_legend)
```

## Motivations by Gender
```{r}
motivations_by_gender <- read_csv(here::here("data/motivations_by_gender.csv")) %>% gather(key = gender, value = percentage, 2:3) 

motivations_by_gender_plot <- ggplot(motivations_by_gender)+
  geom_bar(aes(x = gender, 
               y = percentage, 
               fill= motivation), 
           stat = "identity",
           position = "fill") +
  theme_classic() +
  scale_x_discrete(labels = c("Men (n=122)", "Women (n=166)"))+
  coord_flip()+
  scale_y_continuous(labels=scales::percent)+
  scale_fill_brewer(palette = "GnBu")+
  labs(fill = "Motivators")+
  ggtitle("Women and Men's motivations to participate in SSF associations")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        #axis.title = element_text(face = "bold"),
        axis.text.y =element_text(size = 10),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

motivation_legend <- ggdraw(motivations_plot)+
  draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.9, y=0.02)


plot(motivations_by_gender_plot)
```




#Others
```{r echo = FALSE, message= FALSE, warning= FALSE}
##Activity Men and women

fishers_activity_2016 <- read_csv(here("data/fishers_activity_rpa_2016.csv"))%>%
  group_by(gender) %>% 
  mutate(total_gender = sum(number)) %>% 
  ungroup() %>% 
  mutate(pct_per_gender = (number/total_gender)*100)


fishers_activity_16_plot <- ggplot(fishers_activity_2016)+
  geom_bar(aes(x= gender, 
               y= pct_per_gender/100, 
               fill = Activity),
           stat = "identity")+
  theme_classic()+
  scale_y_continuous(labels=scales::percent)+
  scale_fill_manual(values = c("#C6DBEF", "#7BCCC4", "#4EB3D3", "#2B8CBE"))+
  scale_x_discrete(labels=c("Men (n = 121,634)", "Women (n = 29,952)"))+
  ylab("Percentage of RPA")+
  ggtitle("Percentage of men and women's registers in each fishery activity")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_text(face = "bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 10, color = "black", face = "bold")) #

fishers_activity_legend <- ggdraw(fishers_activity_16_plot)+
  draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.87, y=0.02)


plot(fishers_activity_legend)
```


