---
title: "gender_ssf_data_analysis"
author: "Camila Vargas"
date: "3/22/2020"
output: pdf_document
---

This script analyses data and creates figures for paper "Exploring the relationship between gender and collective action in small scale fisheries associations"

**Authors:** Camila Vargas, Antonella Rivera, Juan Carlos Castilla, Rodrigo A. Estévez , Stefan Gelcich


All the data used here has not been published.


Data was collected in Chile by Camila Vargas Between December 2014 and May 2015.

Raw data sets needed to read this script:
1. __vargas_gender_data_raw.csv__ raw data from surveys collected between December 2014 and May 2015. Each row correspond to 1 survey.

2. __women_men_ssf_chile_yearly.csv__ Number of fishers (women and men) officially registered as an artisanal fisher in Chile from 2004 to 2017. Data source: SERNAPESCA

3. __rpa_associations_yearly.csv__ Number and type (gender composition) of small-scale fisheries association officially registered in Chile from 2004 to 2017. Data source: SERNAPESCA

4. __fishers_activity_rpa.csv__ Number of fishing licenses for each fishing activity, by gender from 2004 to 2017. Data source: SERNAPESCA

5. __fishers_motivations.csv__ fishers' motivations to participate in ssf association. Raw data was clustered in 9 thematic groups. Here the proportion each theme was mention by men and women. Data collected through the surveys between December 2014 and May 2015


6. __data/motivations_by_gender.csv__ fishers' motivations to participate in ssf association. Raw data was clustered in 9 motivations. Here the percentage each theme was mention by men and women. Data collected through the surveys between December 2014 and May 2015



Set Up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(readxl)
library(pgirmess)
library(dunn.test)
library(plotrix)
library(ggrepel)


library(plotrix)
library(RColorBrewer)
library(cowplot) #theme_set(theme_cowplot())
library(ggrepel)
library(scales)
library(knitr)
library(kableExtra)


# my_palette <-  c(brewer.pal(9, "Blues")[c(2,4,6,8)])
# my_palette_2 <- c(brewer.pal(9, "GnBu")[c(4,5,6,7)])
my_palette_3 <- c(brewer.pal(9, "Blues")[3], brewer.pal(9, "GnBu")[c(5,6,7)])
pallet_grey_4 <- gray.colors(4, 1, 0)
pallet_bw_4 <- gray.colors(4, 1, 0)
#my_palette_3:
#"#7BCCC4" verde
#"#4EB3D3" azul mar
#"#2B8CBE" azul oscuro
#"#C6DBEF" celeste
```

## Read raw data

```{r}

gender_raw <- read_csv(here::here("data/vargas_gender_data_raw.csv")) %>% 
  rename(soc_cap_mean = soc_capital)

type_organization <- c("Men", "Women", "MixedW", "MixedM")
n_assos <- c(25,30,29,31)
n_assos_type <- tibble(type_organization, n_assos)

```


#Data Analysis

##Analysis of socio-demographic data 

###Individual-scale variables

A2. Socio-demographic
Fisher's age

```{r}

##calculate the average per type of association
fishers_age_average <- gender_raw %>% 
  group_by(type_organization) %>% 
  summarise(mean = mean(age))

##Is data normally distributed?
hist(gender_raw$age)
qqnorm(gender_raw$age)
shapiro.test(gender_raw$age) ## W = 0.99066, p-value = 0.6254 NORMAL --> ANOVA


##Are there statistical difference?
anova_age <- aov(age~type_organization, data = gender_raw)
summary(anova_age)

#F=0.961  p = 0.414



```

Gear Ownership
```{r}
own_gear <- gender_raw %>% 
  select(type_organization, gear) %>% 
  group_by(type_organization, gear) %>% 
  tally() %>% 
  spread(key = gear, value = n) %>% 
  mutate(Yes = as.numeric(Yes)) %>% 
  mutate(No = as.numeric(No)) %>%
  ungroup() %>% 
  select(Yes, No) 

own_gear <- as.matrix(own_gear)

gear_chi <- chisq.test(own_gear)

gear_chi
#X-squared = 5.2749, df = 3, p-value = 0.1527


gear_pct <- gender_raw %>% 
  select(type_organization, gear) %>% 
  group_by(type_organization, gear) %>% 
  tally() %>% 
  left_join(n_assos_type, by= "type_organization") %>% 
  filter(gear == "Yes") %>% 
  mutate(pct = (n/n_assos)*100)


# gear_men_women <- raw_data %>% 
#   select(gender, gear) %>% 
#   group_by(gender, gear) %>% 
#   tally() %>% 
#   spread(key = gear, value = n) %>% 
#   mutate(Yes = as.numeric(Yes)) %>% 
#   mutate(No = as.numeric(No)) %>%
#   ungroup() %>% 
#   select(Yes, No)
# 
# gear_men_weomen_chi <- chisq.test(gear_men_women)
# #X-squared = 3.5441, df = 1, p-value = 0.05976


```

Education
```{r}
education <- gender_raw %>% 
  select(type_organization, education) %>% 
  group_by(type_organization, education) %>% 
  tally() %>% 
  spread(key = education, value = n) %>% 
  mutate(HigherED = as.numeric(HigherED)) %>% 
  mutate(HighSchool = as.numeric(HighSchool)) %>% 
  mutate(Incomplete = as.numeric(Incomplete)) %>% 
  mutate(No = as.numeric(No)) %>% 
  mutate(primary = as.numeric(primary)) %>% 
  mutate(incomplete_no = sum(Incomplete,No, na.rm = T))%>% 
  ungroup() %>% 
  select(type_organization, HigherED, HighSchool,primary, incomplete_no)

education$HigherED[is.na(education$HigherED)] <- 0



education_pct <- gender_raw %>% 
  select(type_organization, education) %>% 
  group_by(type_organization, education) %>% 
  tally() %>% 
  spread(key = education, value = n) %>% 
  mutate(HigherED = as.numeric(HigherED)) %>% 
  mutate(HighSchool = as.numeric(HighSchool)) %>% 
  mutate(Incomplete = as.numeric(Incomplete)) %>% 
  mutate(No = as.numeric(No)) %>% 
  mutate(primary = as.numeric(primary)) %>% 
  mutate(incomplete_no = sum(Incomplete,No, na.rm = T))%>% 
  ungroup() %>% 
  left_join(n_assos_type, by= "type_organization") %>% 
  select(type_organization, incomplete_no, primary, HighSchool,HigherED, n_assos) %>%
  mutate(HigherED = ifelse(is.na(HigherED), 0, HigherED)) %>% 
  mutate(incomplete_no = (incomplete_no/n_assos)*100) %>% 
  mutate(primary = (primary/n_assos)*100) %>% 
  mutate(HighSchool = (HighSchool/ n_assos)*100) %>% 
  mutate(HigherED = (HigherED/n_assos)*100) %>% 
  mutate(total= incomplete_no+primary+HighSchool+HigherED)
  
  
incomplete_no <- education %>% 
    select(incomplete_no) %>% 
    t()
chi_incomplete_no <- chisq.test(incomplete_no) ##X-squared = 4.92, df = 3, p-value = 0.1777

primary <- education %>% 
  select(primary) %>% 
  t()

chi_primary <- chisq.test(primary) #X-squared = 0.89474, df = 3, p-value = 0.8267

highschool <- education %>% 
  select(HighSchool) %>% 
  t()

chi_highschool <- chisq.test(highschool) #X-squared = 2, df = 3, p-value = 0.5724

higher_ed <- education %>%
  select(HigherED) %>% 
  t()

chi_higher_ed <- chisq.test(higher_ed) #X-squared = 3.8, df = 3, p-value = 0.2839

```


A3. History of Use
Average years RPA

```{r}
year_rpa_average <- gender_raw %>%
  mutate(years_rpa = 2016 - year_rpa) %>% 
  group_by(type_organization) %>% 
  summarise(mean = mean(years_rpa))
  
years_rpa_2016 <- gender_raw %>%
  mutate(years_rpa = 2016 - year_rpa)

##Is data normally distributed?
hist(years_rpa_2016$years_rpa)
qqnorm(years_rpa_2016$years_rpa)
shapiro.test(years_rpa_2016$years_rpa) ## W = 0.97149, p-value = 0.01478 NOT NORMAL -->KW

##Are there statistical difference?

years_rpa_KW <- kruskal.test(years_rpa~ type_organization, data = years_rpa_2016)
##chi-squared = 21.962, df = 3, p-value = 6.642e-05



#post hoc test
years_rpa_post <- kruskalmc(gender_raw$years_rpa, gender_raw$type_organization)


# Multiple comparison test after Kruskal-Wallis 
# p.value: 0.05 
# Comparisons
#                 obs.dif critical.dif difference
# Men-MixedM    14.324516     23.64545      FALSE
# Men-MixedW    31.656552     24.00669       TRUE
# Men-Women     38.010000     23.82073       TRUE
# MixedM-MixedW 17.332036     22.72481      FALSE
# MixedM-Women  23.685484     22.52827       TRUE
# MixedW-Women   6.353448     22.90714      FALSE  
#   
  
```


A8. Importance of resource
Marine resources primary source of income 

```{r}
livelihood <- gender_raw %>% 
  select(type_organization, income_marine_res) %>% 
  group_by(type_organization, income_marine_res) %>% 
  tally() %>% 
  spread(key = income_marine_res, value = n) %>% 
  mutate(Yes = as.numeric(Yes)) %>% 
  mutate(No = as.numeric(No)) %>%
  ungroup() %>% 
  select(Yes, No)

livelihood_chi <- chisq.test(livelihood)

livelihood_chi
#X-squared = 20.314, df = 3, p-value = 0.0001461

# livelihood_men_women <- raw_data %>% 
#   select(gender, income_marine_res) %>% 
#   group_by(gender, income_marine_res) %>% 
#   tally() %>% 
#   spread(key = income_marine_res, value = n) %>% 
#   mutate(Yes = as.numeric(Yes)) %>% 
#   mutate(No = as.numeric(No)) %>%
#   ungroup() %>% 
#   select(Yes, No)

livelihood_pct <- gender_raw %>% 
  select(type_organization, income_marine_res) %>% 
  group_by(type_organization, income_marine_res) %>% 
  tally() %>% 
  filter(income_marine_res == "Yes") %>% 
  ungroup() %>% 
  left_join(n_assos_type, by = "type_organization") %>% 
  mutate(pct= (n/n_assos)*100) %>% 
  select(type_organization)

```


###Association-scale variables

A1. Number of users
Average group size (Number of participants) 

```{r}

members <- gender_raw %>% 
  group_by(type_organization) %>% 
  summarise(mean_n_members = median(n_members_org, na.rm = T))


##Are there statistical difference?
members_KW <- kruskal.test(n_members_org~ type_organization, data = gender_raw)
##Kruskal-Wallis chi-squared = 6.5988, df = 3, p-value = 0.08585 --> NO SIG DIF

```


A3. History of Use
Average age of associations 

```{r}


average_age_assoc <- gender_raw %>% 
  mutate(age_org = 2016 - year_rpa_org) %>% 
  group_by(type_organization) %>% 
  summarise(average_age = mean(age_org))

organization_age <- gender_raw %>% 
  mutate(age_org = 2016 - year_rpa_org)


hist(organization_age$age_org)
qqnorm(organization_age$age_org)
shapiro.test(organization_age$age_org)  
##W = 0.92184, p-value = 4.716e-06 NOT NORMAL


##Are there significant diferences?
org_age_KW <- kruskal.test(age_org~ type_organization, data = organization_age)
#Kruskal-Wallis chi-squared = 48.598, df = 3, p-value = 1.588e-10

#post hoc test
age_org_post <- kruskalmc(organization_age$age_org, organization_age$type_organization)



```


##Evaluation of perceptions

###Indicators based on "norms and trust"

Leadership

```{r}

hist(gender_raw$leadership)
qqnorm(gender_raw$leadership)
shapiro.test(gender_raw$leadership) ## W = 0.73042, p-value = 3.069e-13 NOT NORMAL
  
#Krus-kal wallis
leadership_KW <- kruskal.test(leadership~ type_organization, data = gender_raw)
##Kruskal-Wallis chi-squared = 17.933, df = 3, p-value = 0.0004541 SIGNIFICANT


#post hoc test
leadershio_post <- kruskalmc(gender_raw$leadership, gender_raw$type_organization)

# obs.dif critical.dif difference
# Men-MixedM    21.947742     23.64545      FALSE
# Men-MixedW    32.842069     24.00669       TRUE
# Men-Women     29.830000     23.82073       TRUE
# MixedM-MixedW 10.894327     22.72481      FALSE
# MixedM-Women   7.882258     22.52827      FALSE
# MixedW-Women   3.012069     22.90714      FALSE


```

Entrepreneurship

```{r}

hist(gender_raw$entrepreneurship)
qqnorm(gender_raw$entrepreneurship)
shapiro.test(gender_raw$entrepreneurship) ## W = 0.51912, p-value < 2.2e-16 --> NOT NORMAL
  
#Krus-kal wallis
entrepreneurship_KW <- kruskal.test(entrepreneurship~ type_organization, data = gender_raw)
##Kruskal-Wallis chi-squared = 14.722, df = 3, p-value = 0.002071 SIGNIFICANT



#post hoc test
entrepreneurship_post <- kruskalmc(gender_raw$entrepreneurship, gender_raw$type_organization)


entrep_data <- gender_raw$entrepreneurship
assos_type_data <- gender_raw$type_organization

dunn_entrepreneurship <- dunn.test(entrep_data, assos_type_data)

summary(DunnEntrepreneurship)


#  Comparison of entrep_data by assos_type_data                  
#                                 (No adjustment)                                
# Col Mean-|
# Row Mean |        Men     MixedM     MixedW
# ---------+---------------------------------
#   MixedM |  -2.203620
#          |    0.0138*
#          |
#   MixedW |  -3.324181  -1.218799
#          |    0.0004*     0.1115
#          |
#    Women |  -3.398127  -1.280182  -0.049910
#          |    0.0003*     0.1002     0.4801
# 
# alpha = 0.05
# Reject Ho if p <= alpha/2



```



Participation in Activities

```{r}

hist(gender_raw$activities)
qqnorm(gender_raw$activities)
shapiro.test(gender_raw$activities) ## W = 0.78721, p-value = 3.325e-11 NOT NORMAL
#Krus-kal wallis

activity_KW <- kruskal.test(activities~ type_organization, data = gender_raw)
##Kruskal-Wallis chi-squared = 21.728, df = 3, p-value = 7.431e-05 --> SIGNIFICANT


#post hoc test
activities_post <- kruskalmc(gender_raw$activities, gender_raw$type_organization)

#                 obs.dif critical.dif difference
# Men-MixedM    18.734074     22.93514      FALSE
# Men-MixedW    29.371538     23.14622       TRUE
# Men-Women     35.660000     22.37703       TRUE
# MixedM-MixedW 10.637464     22.70497      FALSE
# MixedM-Women  16.925926     21.92030      FALSE
# MixedW-Women   6.288462     22.14106      FALSE


```



Trust

```{r}

hist(gender_raw$trust)
qqnorm(gender_raw$trust)
shapiro.test(gender_raw$trust) ## W = 0.91049, p-value = 1.107e-06 NOT NORMAL

#Krus-kal wallis

trust_KW <- kruskal.test(trust~ type_organization, data = gender_raw)
##Kruskal-Wallis chi-squared = 4.1494, df = 3, p-value = 0.2458 --> NOT SIGNIFICANT



```



Norms Compliance

```{r}

hist(gender_raw$norms)
qqnorm(gender_raw$norms)
shapiro.test(gender_raw$norms) ## W = 0.86909, p-value = 1.184e-08 NOT NORMAL

#Krus-kal wallis

norms_KW <- kruskal.test(norms ~  type_organization, data = gender_raw)
## Kruskal-Wallis chi-squared = 3.9024, df = 3, p-value = 0.2722 --> NOT SIGNIFICANT

```



Social Capital


```{r}

hist(gender_raw$soc_cap_mean)
qqnorm(gender_raw$soc_cap_mean)
shapiro.test(gender_raw$soc_cap_mean) ## W = 0.98708, p-value = 0.3423 NORMAL

#Krus-kal wallis

soc_capital_KW <- kruskal.test(soc_cap_mean ~  type_organization, data = gender_raw)
## Kruskal-Wallis chi-squared = 6.7174, df = 3, p-value = 0.08147


##ANOVA
##Are there statistical difference?
anova_soc_capital <- aov(soc_cap_mean~type_organization, data = gender_raw)
summary(anova_age)

#  Df Sum Sq Mean Sq F value Pr(>F)
# type_organization   3    364   121.2   0.961  0.414
# Residuals         111  14004   126.2  

```


###Social Performance indicators

Efficiency
```{r}

hist(gender_raw$efficiency)
qqnorm(gender_raw$efficiency)
shapiro.test(gender_raw$efficiency) ## W = 0.82474, p-value = 2.259e-10 NOT NORMAL

#Krus-kal wallis

efficiency_KW <- kruskal.test(efficiency~ type_organization, data = gender_raw)
##Kruskal-Wallis chi-squared = 25.158, df = 3, p-value = 1.431e-05 --SIGNIFICANT


#post hoc test
effciency_post <- kruskalmc(gender_raw$efficiency, gender_raw$type_organization)

#   obs.dif critical.dif difference
# Men-MixedM    28.829032     23.64545       TRUE
# Men-MixedW    30.941379     24.00669       TRUE
# Men-Women     42.650000     23.82073       TRUE
# MixedM-MixedW  2.112347     22.72481      FALSE
# MixedM-Women  13.820968     22.52827      FALSE
# MixedW-Women  11.708621     22.90714      FALSE


```


Cooperation
```{r}

hist(gender_raw$cooperation)
qqnorm(gender_raw$cooperation)
shapiro.test(gender_raw$cooperation) ## W = 0.83741, p-value = 6.509e-10 NOT NORMAL

#Krus-kal wallis

cooperation_KW <- kruskal.test(cooperation~ type_organization, data = gender_raw)
##Kruskal-Wallis chi-squared = 14.372, df = 3, p-value = 0.002441  --> SIGNIFICANT


#post hoc test
cooperation_post <- kruskalmc(gender_raw$cooperation, gender_raw$type_organization)

#  obs.dif critical.dif difference
# Men-MixedM    12.889032     23.64545      FALSE
# Men-MixedW    30.363448     24.00669       TRUE
# Men-Women     25.410000     23.82073       TRUE
# MixedM-MixedW 17.474416     22.72481      FALSE
# MixedM-Women  12.520968     22.52827      FALSE
# MixedW-Women   4.953448     22.90714      FALSE

```


Conflict Resolution

```{r}

hist(gender_raw$conflict)
qqnorm(gender_raw$conflict)
shapiro.test(gender_raw$conflict) ##W = 0.91765, p-value = 2.978e-06  NOT NORMAL

#Krus-kal wallis

conflict_KW <- kruskal.test(conflict ~  type_organization, data = gender_raw)
## Kruskal-Wallis chi-squared = 2.7268, df = 3, p-value = 0.43572 --> NOT SIGNIFICANT

```


#Figures

##Methods

###Figure 1: Women participation in ssf in Chile

```{r Women participation in ssf in Chile, echo = FALSE, warning=FALSE, message=FALSE, fig.cap= 'Women participation in small-scale fisheires in Chile. A) Percentage of women officially registered in the National Fisheries Service (RPA) through time.  B) Number of mixed gender, only-women and only men associations oficially registered per year.Data source: SERNAPESCA, 2017.'}

##Percentage of women in ssf from 2004 to 2016

rpa_yearly_women <- read_csv(here("data/women_men_ssf_chile_yearly.csv")) %>% 
  select(year, pct_women) %>% 
  filter(year == 2004:2016)
  
pct_women_plot <- ggplot(rpa_yearly_women, aes(x= year, y= pct_women/100))+
  geom_line(color = "#7BCCC4", size = 1.5)+
  theme_classic()+
  scale_x_continuous(breaks = seq(2004, 2016, 1))+
  scale_y_continuous(labels=scales::percent)+
  xlab("Year")+
  ylab("Percentage of women")+
  theme(axis.title = element_text(size = 10, face = "bold"))
  
#plot(pct_women_plot)


##RPA Associations by gender

rpa_association <- read.csv(here("data/rpa_associations_yearly.csv")) %>% 
  select(-total) %>% 
  gather(key = Gender, value = number, 2:4) %>% 
  mutate(Gender = fct_relevel(Gender,"Women", "Men", "Mixed")) %>% 
  filter(year!=2017)

association_plot <- ggplot(rpa_association)+
  geom_bar(aes(x= year, y= number, fill = Gender), stat = "identity")+
  theme_classic()+
  scale_fill_manual(values = c("#7BCCC4", "#C6DBEF","#4EB3D3"))+ #2B8CBE
  labs(y= "Number of associations", x="Year")+
  scale_x_continuous(breaks = seq(2004, 2016, 1))+
  theme(axis.title = element_text(size = 10, face = "bold"),
         legend.position="bottom", 
        legend.box = "horizontal")
        #axis.text.x = element_text(angle = 30))

##axis.text.x = element_text(size = 10, color = "black")

#plot(association_plot)

title_figure_method <- ggdraw() + draw_label("Women Participation in Small-scale Fisheries in Chile", fontface='bold')

figure_method <- plot_grid(pct_women_plot,association_plot, labels = c("A", "B"), nrow= 2 , align = "v")

#plot(figure_method)


figure_method_title <- plot_grid(title_figure_method, figure_method, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
  #draw_label("Data Source: SERNAPESCA, 2017", size = 9, fontface = "italic", x=0.87, y=0.03)

plot(figure_method_title)

##ggplot2::ggsave("women_ssf_chile.png", plot = figure_method_title)
```


### Figure2: Percentage of men and women registers in each fishery activity

```{r, licencse under each activity, echo = FALSE, warning=FALSE, message=FALSE, fig.cap= ': Percentage of licenses registered to  men (n= 121,634) and women (n=29,952) subscribed under each small-scale fishery activity. Total number of licenses are higher than number of fishers officially registered because activities are not mutually exclusive. Data source: SERNAPESCA 2016'}

##Activity Men and women

fishers_activity_2016 <- read_csv(here("data/fishers_activity_rpa.csv"))%>%
   filter(year == 2016) %>% 
  group_by(gender) %>% 
  mutate(total_gender = sum(number)) %>% 
  ungroup() %>% 
  mutate(pct_per_gender = (number/total_gender)*100) %>% 
  mutate(Activity = ifelse(Activity=="Gleaner", "Shore gatherer", Activity))
 


fishers_activity_16_plot <- ggplot(fishers_activity_2016)+
  geom_bar(aes(x= gender, 
               y= pct_per_gender/100, 
               fill = Activity),
           stat = "identity",
           colour = "black",
           width = 0.6)+
  theme_classic(base_size = 18)+
  scale_y_continuous(labels=scales::percent)+
  coord_flip()+
  scale_fill_manual(values = c("#FFFFFF","#000000", "#D4D4D4","#9B9B9B" ))+
  #scale_fill_manual(values = c("#FFFFFF", "#D4D4D4", "#9B9B9B", "#000000"))+
  #scale_fill_manual(values = c("#C6C6C6","#E6E6E6", "#666666", "#9F9F9F"))+ #gray colors
  #scale_fill_manual(values = c("#C6DBEF", "#7BCCC4", "#4EB3D3", "#2B8CBE"))+
  scale_x_discrete(labels=c("Men (n = 121,634)", "Women (n = 29,952)"))+
  ylab("Percentage of RPA")+
  ggtitle("Percentage of male and female's registers by license type")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.text.y = element_text(size = 15, color = "black"))

# fishers_activity_legend <- ggdraw(fishers_activity_16_plot)+
#   draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.87, y=0.02)


plot(fishers_activity_16_plot)

ggsave("fig1.tiff", units="in", width=7, height=4, dpi=360)


```

###Figure 3: Map with locations
See ppt

##Results

###Figure 4: Motivations

We did not used this plot!
```{r}
motivations <- read_csv(here::here("data/fishers_motivations.csv")) %>% 
  gather(key = Gender, value = percentage, 2:3) 

##Needs n for ech thematic group
motivations_plot <- ggplot(motivations)+
  geom_bar(aes(x = Motivation, 
               y = percentage, 
               fill=Gender), 
           stat = "identity",
           position = "fill",
           width = 0.7)+
  coord_flip()+
  scale_y_continuous(labels=scales::percent)+
  scale_fill_manual(values = c("#4EB3D3", "#7BCCC4"),
                    label = c("Men (n = 53)", "Women (n = 62)"), "Gender")+
  ylab("Percentage")+
  ggtitle("Women and Men's motivations to participate in SSF associations")+
  theme(plot.title = element_text(hjust = 0.5),
        axis.title = element_text(face = "bold"),
        axis.text.y =element_text(size = 10))

motivation_legend <- ggdraw(motivations_plot)+
  draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.9, y=0.02)

plot(motivations_plot)
plot(motivation_legend)
```

**Instead we used:**
Motivations by Gender
```{r}
motivations_by_gender <- read_csv(here::here("data/motivations_by_gender.csv")) %>% gather(key = gender, value = percentage, 2:3) %>% 
  mutate(motivation = ifelse(motivation== "Access to MEABR", "Access to TURF", motivation))

motivations_by_gender_plot <- ggplot(motivations_by_gender)+
  geom_bar(aes(x = gender, 
               y = percentage, 
               fill= motivation), 
           stat = "identity",
           position = "fill") +
  theme_classic(base_size = 16) +
  scale_x_discrete(labels = c("Men (n=122)", "Women (n=166)"))+
  coord_flip()+
  scale_y_continuous(labels=scales::percent)+
  #scale_fill_manual(values = c("#FFFFFF","#F0F0F0","#E0E0E0","#CECECE", "#BABABA", "#A3A3A3", "#888888", "#636363", "#000000"))+
 # scale_fill_manual(values = c("#B3B3B3" ,"#A8A8A8", "#9D9D9D" ,"#909090", "#828282", "#727272" ,"#5F5F5F","#454545", "#000000"))+
  scale_fill_manual(values = c("#E6E6E6" ,"#D8D8D8" ,"#C9C9C9" ,"#B9B9B9", "#A7A7A7", "#939393" ,"#7A7A7A","#595959" ,"#000000"))+
  #scale_fill_grey(0, 1, name = "Motivations")+
  #scale_fill_brewer(palette = "GnBu")+
  labs(fill = "Motivators")+
  ggtitle("Women and Men's motivations to participate in SSF associations")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        #axis.title = element_text(face = "bold"),
        axis.text.y =element_text(size = 18),
        axis.text.x =element_text(size = 18),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12))

# motivation_legend <- ggdraw(motivations_plot)+
#   draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.9, y=0.02)

plot(motivations_by_gender_plot)

ggsave("fig4.tiff", units="in", width=10, height=4, dpi=360)

```


###Figure 5: Perception on Association related variables

Fig caption: Results from Kruskal-Wallis test showed significant differences in Leadership "(p= 0.0005)", Entrepreneurship "(p=0.002)", Participation in Activities "(p=<0.0001)", but not in Trust "(p=0.245)", Norm accomplishments "(p=0.272)", Social Capital "(p=0.08)". Letters on the top of the bars represent Dunn’s posteriori tests' results.

```{r association level vriables,  echo = FALSE, warning=FALSE, message=FALSE, fig.cap= 'Average degree in which groups perceive association-level variables relevant for collective action. Scores go from 0 (nothing at all) to 20 (very much).'}


## Average degree in which pariticipants percieve group attributes.

##calcualting mean, sd and se
assoc_scale_summary <- gender_raw %>% 
  select("Type of Association"= type_organization, 
         Leadership = leadership, 
         Entrepreneurship = entrepreneurship, 
         "Participation in Activities" = activities, 
         Trust = trust, 
         "Compliance" = norms, 
         "Social Capital" = soc_cap_mean) %>% 
  pivot_longer(cols = 2:7,
               names_to = "attribute",
               values_to = "value") %>% 
  group_by(`Type of Association`, attribute) %>% 
  #mutate(N = n()) %>% ## adds the n for each type of association
  summarise_all(funs(mean, sd, std.error), na.rm = TRUE) %>% 
  ungroup() %>% 
  mutate( `Type of Association` = recode(`Type of Association`, MixedM = "Mixed - M (n=31)", MixedW = "Mixed - W (n=29)", Men = "Men (n=25)", Women = "Women (n=30)")) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Women (n=30)" & attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities"), "a",NA )) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Men (n=25)" & attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities"), "b",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - W (n=29)" & attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities"), "a",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - M (n=31)" & attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities"), "ab",signif_diff)) %>% 
   mutate("Type of Association" = fct_relevel(`Type of Association`, c("Women (n=30)", "Men (n=25)", "Mixed - W (n=29)", "Mixed - M (n=31)")),
         attribute = fct_relevel(attribute, c("Leadership", "Entrepreneurship", "Participation in Activities", "Trust", "Compliance", "Social Capital")))

  
View(assoc_scale_summary)


#plot (Social Capital; Entrepreneur; Leadership)

signficant_diff <- ggplot(assoc_scale_summary %>% 
                              filter(attribute %in% c("Leadership", "Entrepreneurship","Participation in Activities")),
                            aes(`Type of Association`, mean)) +
  geom_bar(aes(fill=`Type of Association`), colour="black", stat = "identity") +
  geom_errorbar(aes(ymin = mean - std.error, ymax = mean +std.error), width=0.2) +
  geom_text_repel(aes(y=mean+std.error, label = signif_diff), 
                  nudge_y = 0.5,
                  nudge_x = 0.12,
                  direction = "x",
                  vjust = 0,
                  hjust = 0.5,
                  segment.colour = "transparent")+

    # geom_text_repel(aes(y=mean+sd+0.2, label = signif_diff), 
  #                 nudge_y = 0.2,
  #                 direction = "y",
  #                 vjust = 0.5,
  #                 hjust = 0.5,
  #                 segment.colour = "transparent")+
  #geom_hline(yintercept = 10, linetype = "dotted")+ # dotted vrtical line in 10
  theme_classic(base_size = 18) +
  facet_wrap(~attribute) +
  scale_fill_manual(values = c("#FFFFFF","#9B9B9B", "#D4D4D4", "#000000"))+
  #scale_fill_manual(values = c("#7BCCC4", "#4EB3D3", "#2B8CBE", "#C6DBEF"))+
  #scale_fill_brewer(palette = "BuGn")+ #find a good color
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position="none", 
        legend.box = "horizontal")

plot(signficant_diff)


no_diff <- ggplot(assoc_scale_summary %>% 
                              filter(attribute %in% c("Compliance", "Social Capital","Trust")),
  aes(`Type of Association`, mean)) +
   geom_bar(aes(fill=`Type of Association`), colour="black", stat = "identity") +
   geom_errorbar(aes(ymin = mean - std.error, ymax = mean +std.error), width=0.2) +
  #geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width=0.2) +
  #geom_hline(yintercept = 10, linetype = "dotted")+
  theme_classic(base_size = 18) +
  facet_wrap(~attribute) +
  scale_fill_manual(values = c("#FFFFFF","#9B9B9B", "#D4D4D4", "#000000"))+
  #scale_fill_manual(values = c("#7BCCC4", "#4EB3D3", "#2B8CBE", "#C6DBEF"))+
  #scale_fill_brewer(palette = "BuGn")+ #find a good color
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position="bottom", 
        legend.box = "horizontal")+
  expand_limits(y = 20)
  #labs(caption = "(Vargas et al, unpublished data)", element_text(face = "italic", size = 7))

##Both plot plotted together
figure_assoc_att <- plot_grid(signficant_diff, no_diff, labels = c("A", "B"), nrow = 2, align = "v")

## Figure in manuscript
plot(figure_assoc_att)

ggsave("fig5.tiff", units="in", width=10, height=7, dpi=360)


## Other additions
# title_figure_assoc_att <-  ggdraw() + draw_label("Perception on association related variables", fontface='bold')
# 
# figure_assoc_att_legend <- ggdraw(figure_assoc_att)+
#   draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.9, y=0.02)
# 
# figure_assoc_att_title <- plot_grid(title_figure_assoc_att, figure_assoc_att_legend, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
# 
# plot(figure_assoc_att_title)


```


###Perception on social performance variable

Fig caption
Average degree in which groups evaluate social performance indicators: Efficiency (p<0,0001); (Cooperation p=0,002) and (Conflict Resolution p=0,436). Scores go from 0 (nothing at all) to 20 (very much). Significant differences are represented by different letters and analyzed with Kruskal-Wallis test and Dunn’s posteriori tests.


```{r  Social performance vriables,  echo = FALSE, warning=FALSE, message=FALSE, fig.cap='hola'}
#Average degree in which groups evaluate social performance indicators


soc_perform_summary<- gender_raw %>% 
  select("Type of Association"= type_organization, Efficiency = efficiency, Cooperation = cooperation, "Conflict Resolution" = conflict) %>%
  pivot_longer(cols = 2:4,
               names_to = "attribute",
               values_to = "value") %>% 
  group_by(`Type of Association`, attribute) %>% 
  #group_by(N = n(), add = TRUE) %>% ## adds the n for each type of association
  summarise_all(funs(mean, sd, std.error), na.rm = TRUE) %>% 
  ungroup() %>% 
  mutate( `Type of Association` = recode(`Type of Association`, MixedM = "Mixed - M (n=31)", MixedW = "Mixed - W (n=29)", Men = "Men (n=25)", Women = "Women (n=30)")) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Women (n=30)" & attribute %in% c("Efficiency", "Cooperation"), "a",NA )) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Men (n=25)" & attribute %in% c("Efficiency", "Cooperation"), "b",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - W (n=29)" & attribute %in% c("Efficiency", "Cooperation"), "a",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - M (n=31)" & attribute == "Cooperation", "ab",signif_diff)) %>% 
  mutate(signif_diff = ifelse(`Type of Association` == "Mixed - M (n=31)" & attribute == "Efficiency", "a",signif_diff)) %>% 
  mutate("Type of Association" = fct_relevel(`Type of Association`, c("Women (n=30)", "Men (n=25)", "Mixed - W (n=29)", "Mixed - M (n=31)")),
         attribute = fct_relevel(attribute, c("Efficiency", "Cooperation", "Conflict Resolution")))
  
View(soc_perform_summary)


soc_perform_plot<- ggplot(soc_perform_summary, aes(`Type of Association`, mean)) +
   geom_bar(aes(fill=`Type of Association`), colour= "black", stat = "identity") +
  geom_errorbar(aes(ymin = mean - std.error, ymax = mean +std.error), width=0.2) +
  geom_text_repel(aes(y=mean+std.error, label = signif_diff), 
                  nudge_y = 0.5,
                  nudge_x = 0.12,
                  direction = "x",
                  vjust = 0,
                  hjust = 0.5,
                  segment.colour = "transparent")+
  #geom_hline(yintercept = 10, linetype = "dotted")+ #color = "gray"
  theme_classic(base_size = 18) +
  facet_wrap(~attribute) +
  scale_fill_manual(values = c("#FFFFFF","#9B9B9B", "#D4D4D4", "#000000"))+
  #scale_fill_manual(values = c("#7BCCC4", "#4EB3D3", "#2B8CBE", "#C6DBEF"))+
  #scale_fill_viridis(discrete = T, option = "D")+
  #scale_fill_brewer(palette = "BuGn")+ #find a good color
  #ggtitle ("Small-scale Fisher's Perception variables of social performance outcomes of their associatons")+
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position="bottom", 
        legend.box = "horizontal")+
  expand_limits(y = 20) #y-axis goes to up to 20
  

plot(soc_perform_plot)
ggsave("fig6.tiff", units="in", width=10, height= 4, dpi=360)


# title_soc_perform <- ggdraw()+draw_label("Perception on social performance variables", fontface='bold')
# 
#  
# soc_perf_legend <- ggdraw(soc_perform_plot)+
#   draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.9, y=0.02)
# 
# soc_per_plot_title <- plot_grid(title_soc_perform, soc_perf_legend, ncol=1, rel_heights=c(0.1, 1)) 
# 
# 
# plot(soc_per_plot_title)
```


###Others

```{r echo = FALSE, message= FALSE, warning= FALSE}
##Activity Men and women

fishers_activity_2016 <- read_csv(here("data/fishers_activity_rpa.csv"))%>%
  filter(year == 2016) %>% 
  group_by(gender) %>% 
  mutate(total_gender = sum(number)) %>% 
  ungroup() %>% 
  mutate(pct_per_gender = (number/total_gender)*100)


fishers_activity_16_plot <- ggplot(fishers_activity_2016)+
  geom_bar(aes(x= gender, 
               y= pct_per_gender/100, 
               fill = Activity),
           stat = "identity")+
  theme_classic()+
  scale_y_continuous(labels=scales::percent)+
  scale_fill_manual(values = c("#C6DBEF", "#7BCCC4", "#4EB3D3", "#2B8CBE"))+
  scale_x_discrete(labels=c("Men (n = 121,634)", "Women (n = 29,952)"))+
  ylab("Percentage of RPA")+
  ggtitle("Percentage of men and women's registers in each fishery activity")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_text(face = "bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 10, color = "black", face = "bold")) #

fishers_activity_legend <- ggdraw(fishers_activity_16_plot)+
  draw_label("Vargas et al, unpublished data", size = 9, fontface = "italic", x=0.87, y=0.02)


plot(fishers_activity_legend)
```


##Figure:Activity through time

```{r}
fishers_activity <- read_csv(here("data/fishers_activity_rpa.csv")) %>% 
  mutate(Activity = ifelse(Activity == "Gleaner", "Shore Gatherer", Activity)) %>% group_by(year, Activity) %>% 
  mutate(total_activity = sum(number)) %>% 
  rename(Gender = gender)

shore_gatherers_plot<- ggplot(fishers_activity %>% 
                              filter(Activity == "Shore Gatherer"))+
  geom_bar(aes(x= year, 
               y= number, 
               fill = Gender),
           stat = "identity")+
  theme_classic()+
  scale_fill_manual(values = c("#C6DBEF", "#7BCCC4", "#4EB3D3", "#2B8CBE"))+
  ylab("Total Number of Shore Gatherer Licences")+
  scale_x_continuous(breaks = seq(2004, 2017, 1))+
  #ggtitle("Percentage of men and women's registers in each fishery activity")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_text(face = "bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 10, color = "black"),
        legend.position="bottom", 
        legend.box = "horizontal")


```


##Combining activity with total number of women

```{r}

fisher_women_yearly <- read_csv(here("data/women_men_ssf_chile_yearly.csv")) %>% 
  select(year, women)


gatherer_yearly <- read_csv(here("data/fishers_activity_rpa.csv")) %>% 
  mutate(Activity = ifelse(Activity == "Gleaner", "Shore Gatherer", Activity)) %>% group_by(year, Activity) %>% 
  filter(Activity == "Shore Gatherer") %>% 
  rename(Gender = gender) %>% 
  full_join(fisher_women_yearly, by = "year")
  
combine_plot_gatherer <- ggplot(gatherer_yearly)+
  geom_bar(aes(x= year, 
               y= number, 
               fill = Gender),
               stat = "identity")+
  geom_line(aes(x=year, y=women), color = "red", size = 1.5)+
  theme_classic()+
  scale_fill_manual(values = c("#C6DBEF", "#7BCCC4", "#4EB3D3", "#2B8CBE"))+
  ylab("Number of Licences")+
  ggtitle("Number of Shore Gatherer Licences by gender and Total Number of Women")+
  scale_x_continuous(breaks = seq(2004, 2017, 1))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_text(face = "bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 10, color = "black"),
        legend.position="bottom", 
        legend.box = "horizontal")
  


```


```{r}

boat_owner_yearly <- read_csv(here("data/fishers_activity_rpa.csv")) %>% 
  filter(Activity == "Boat owner") %>% 
  rename(Gender = gender) %>% 
  full_join(fisher_women_yearly, by = "year")
  
combine_plot_boat_owner <- ggplot(boat_owner_yearly)+
  geom_bar(aes(x= year, 
               y= number, 
               fill = Gender),
               stat = "identity")+
  geom_line(aes(x=year, y=women), color = "red", size = 1.5)+
  theme_classic()+
  scale_fill_manual(values = c("#C6DBEF", "#7BCCC4", "#4EB3D3", "#2B8CBE"))+
  ylab("Number of Licences")+
  ggtitle("Number of Boat Owner Licences by gender and Total Number of Women")+
  scale_x_continuous(breaks = seq(2004, 2017, 1))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_text(face = "bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 10, color = "black"),
        legend.position="bottom", 
        legend.box = "horizontal")
  
```

