---
title: "Gender and SSF in Chile Results"
author: "Camila Vargas"
date: "12/15/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(readxl) #install.packages('readxl')
library(freeR)
```

## Read data
```{r}
#social_capital_average <- read_csv(here("data/social_capital_average.csv"))

raw_data_1 <- read_excel(here("data/vargas_gender_data_raw.xlsx"), range ="A1:AG116")

## Raw data fixed - the raw file contains the average for social capital
# mutate(activities = as.numeric(activities),
#          conflict = as.numeric(conflict))
  #left_join(social_capital_average, by= "folio") ##OJO!! social_capital_average


```


## Analysis of socio-demographic data 


Fisher's age (average of association)
```{r}

fishers_age_average <- raw_data %>% 
  group_by(type_organization) %>% 
  summarise(mean = mean(age))

##Are there statistical difference?
anova_age <- aov(age~type_organization, data = raw_data)
summary(anova_age)

#F=0.961  p = 0.414

```

Own gear
```{r}
own_gear <- raw_data %>% 
  select(type_organization, gear) %>% 
  group_by(type_organization, gear) %>% 
  tally() %>% 
  spread(key = gear, value = n) %>% 
  mutate(Yes = as.numeric(Yes)) %>% 
  mutate(No = as.numeric(No)) %>%
  ungroup() %>% 
  select(Yes, No)

own_gear <- as.matrix(own_gear)

gear_chi <- chisq.test(own_gear)

gear_chi
#X-squared = 5.2749, df = 3, p-value = 0.1527


gear_men_women <- raw_data %>% 
  select(gender, gear) %>% 
  group_by(gender, gear) %>% 
  tally() %>% 
  spread(key = gear, value = n) %>% 
  mutate(Yes = as.numeric(Yes)) %>% 
  mutate(No = as.numeric(No)) %>%
  ungroup() %>% 
  select(Yes, No)

gear_men_weomen_chi <- chisq.test(gear_men_women)
#X-squared = 3.5441, df = 1, p-value = 0.05976


```

Education
```{r}
education_men_women <- raw_data %>% 
  select(gender, education) %>% 
  group_by(gender, education) %>% 
  tally() %>% 
  spread(key = education, value = n)

```



Complete primary school
Complete high school
Complete higher education

A3. History of Use
Average years RPA

A8. Importance of resource
Marine resources primary source of income 

```{r}
livelihood <- raw_data %>% 
  select(type_organization, income_marine_res) %>% 
  group_by(type_organization, income_marine_res) %>% 
  tally() %>% 
  spread(key = income_marine_res, value = n) %>% 
  mutate(Yes = as.numeric(Yes)) %>% 
  mutate(No = as.numeric(No)) %>%
  ungroup() %>% 
  select(Yes, No)



livelihood_chi <- chisq.test(livelihood)

livelihood_chi
#X-squared = 20.314, df = 3, p-value = 0.0001461

livelihood_men_women <- raw_data %>% 
  select(gender, income_marine_res) %>% 
  group_by(gender, income_marine_res) %>% 
  tally() %>% 
  spread(key = income_marine_res, value = n) %>% 
  mutate(Yes = as.numeric(Yes)) %>% 
  mutate(No = as.numeric(No)) %>%
  ungroup() %>% 
  select(Yes, No)

livelihood_men_weomen_chi <- chisq.test(livelihood_men_women)

livelihood_men_weomen_chi

```



Association scale
A1. Number of users
Average group size (Number of participants) 

A3. History of Use
Average age of associations 

```{r}
association_age <- read_csv(here::here("data/association_age.csv")) 

average_age_assoc <- association_age %>% 
  group_by(type_organization) %>% 
  summarise(average_age = mean(age_association))

shapiro.test(association_age$age_association)  
##W = 0.93563, p-value = 0.1447 NORMAL

anova_age_assoc <- aov(age_association~type_organization, data = association_age)
summary(anova_age_assoc)

#  Df Sum Sq Mean Sq                     F value Pr(>F)  
# type_organization  3   1351   450.5   4.463 0.0156 * SIGNIFICANT
# Residuals         19   1918   100.9 

#Pst-hoc Tukey Age association
pst_hoc_age_assoc <- TukeyHSD(anova_age_assoc, "type_organization")
pst_hoc_age_assoc

# $type_organization
#                       diff       lwr        upr     p adj
# Mixed-M-Men      -7.266667 -24.37311  9.8397740 0.6375913 No
# Mixed-W-Men     -16.600000 -33.70644  0.5064406 0.0590662 No
# Women-Men       -19.933333 -37.03977 -2.8268927 0.0190074 *
# Mixed-W-Mixed-M  -9.333333 -25.64368  6.9770178 0.3973643 NO
# Women-Mixed-M   -12.666667 -28.97702  3.6436845 0.1636825 NO
# Women-Mixed-W    -3.333333 -19.64368 12.9770178 0.9384483 NO





```


Table 1
```{r indicator description, echo = FALSE, message= FALSE, warning= FALSE}

##import data
indicator_description <- read_csv(here("data/indicators_description.csv"))

options(knitr.table.format = "latex")
options(knitr.kable.NA = '') ## remove NA

knitr::kable(indicator_description, 
             col.names = c("Diagnostic framework component", "Indicator", "Description"), 
             #format.args = list(decimal.mark = '.', big.mark = ","),"latex", 
             booktabs = T, 
             caption= 'Description of indicators evaluated in our study regarding each of the selected variables, under two components of the SES framework') %>% 
kable_styling(latex_options = 'hold_position') %>% 
# column_spec(3, width = "3cm")# wraps text



```

